Graphical representation example: Alternative interpretations

### 2023-11-22 notebooks/Graphical_representation_alternatives.Rmd
Versions introduction of the "Representation int the latent space" section

>>>>

# Representation in the latent space instead of the test space

It is a concern that the multidimensional parameters should be defined
(according to Reckase's, -@reckase_difficulty_1985 definition), in the latent
space. All the computations (both the ones here and in the draft) assume that
the representation of the vectors are in the test space, after arguing that this
should be the correct representation instead of the one in the latent space.

It should be argued (probably more clearly in the draft) that the fact that
Reckase proposes the representation in the latent space may be due to the
confusion resulting from considering that both constitute a single entity. This
is because in the orthogonal case they overlap, making them indistinguishable in
practice.

Let's try to represent these sample items in the latent space, in order to
explore this representation.
